A Distributed Segment-based Approach for Topology-agnostic Nano Networks Routing

### 2013-08-18 PAPER/disr.tex
Added missing '}' character at the end of a 'subsection' definition

\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}
When received, if the node status is \emph{tvisited} with a segID corresponding to the one indicated in
the packet, the node learns to belong to the segment associated to the
id. Further, it should forward this packet to the link where the
original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
can learn the segment id they belong to.  LED shoud be
updated: The state of the node changes from \emph{tvisited} to \emph{visited}.  the
\emph{link\_tvisited} previously set with the segID should be invalidated the
\emph{link\_visited} variable associated to the incoming confirm should be set
as segID. Note that if the request was flooded across different links,
the \emph{link\_visited} variable associated to the other paths shouldn’t be
set.  the \emph{link\_visited} variable associated to the link from which the
request was originated should be set segID

>>>>

\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}}
When received, if the node status is \emph{tvisited} with a segID corresponding to the one indicated in
the packet, the node learns to belong to the segment associated to the
id. Further, it should forward this packet to the link where the
original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
can learn the segment id they belong to.  LED shoud be
updated: The state of the node changes from \emph{tvisited} to \emph{visited}.  the
\emph{link\_tvisited} previously set with the segID should be invalidated the
\emph{link\_visited} variable associated to the incoming confirm should be set
as segID. Note that if the request was flooded across different links,
the \emph{link\_visited} variable associated to the other paths shouldn’t be
set.  the \emph{link\_visited} variable associated to the link from which the
request was originated should be set segID
